Differences in outcomes for patients experiencing left vs. right hemisphere ICH

### 2024-02-14 reports/aggressiveness.qmd
neurosurgery models done

```{r setup, output=FALSE, message=FALSE, warning=FALSE}
library(targets)
library(skimr)
library(dplyr)
library(gt)
library(gtsummary)
library(ggplot2)
library(ggdag)
library(dagitty)
library(marginaleffects)
library(modelsummary)
library(MetBrewer)

@@

# load all targets objects
tar_load_everything()

@@

### Priors

>>>>

```{r setup, output=FALSE, message=FALSE, warning=FALSE}
library(targets)
library(skimr)
library(dplyr)
library(gt)
library(gtsummary)
library(ggplot2)
library(ggdist)
library(gghalves)
library(ggdag)
library(scales)
library(dagitty)
library(marginaleffects)
library(modelsummary)

@@

# load all targets objects
# tar_load_everything()
tar_load(non_surgery_trials)
tar_load(table_1_non_surgery)
tar_load(table_2_non_surgery)
tar_load(aggressive_dag)

@@

### Neurosurgical Intervention

There are two models we will run here: 1) the minimally-sufficient adjustment model, 2) the canonical adjustment model

#### Model

tar_load(neurosurgery_evac_min)

predictions(neurosurgery_evac_min, by = "ich_laterality")

plot_predictions(neurosurgery_evac_min, condition = "ich_laterality") +
  labs(x = "ICH Laterality", y = "Probability of Neurosurgery")

# Format things as percentage points
label_pp <- label_number(
  accuracy = 1, scale = 100,
  suffix = " pp.", style_negative = "minus"
)

label_pp_tiny <- label_number(
  accuracy = 0.01, scale = 100,
  suffix = " pp.", style_negative = "minus"
)

theme_clean <- function() {
  theme_minimal(base_family = "Barlow Semi Condensed") +
    theme(
      panel.grid.minor = element_blank(),
      plot.title = element_text(family = "BarlowSemiCondensed-Bold"),
      axis.title = element_text(family = "BarlowSemiCondensed-Medium"),
      strip.text = element_text(
        family = "BarlowSemiCondensed-Bold",
        size = rel(1), hjust = 0
      ),
      strip.background = element_rect(fill = "grey80", color = NA)
    )
}

avg_comparisons(neurosurgery_evac_min, variables = "ich_laterality") |>
  posterior_draws() |>
  ggplot(aes(x = draw)) +
  stat_halfeye(
    .width = c(0.8, 0.95), point_interval = "median_hdi",
    fill = "#bc3032"
  ) +
  scale_x_continuous(labels = label_pp) +
  labs(
    x = "Effect of hemispheric laterality\n on the probability of receiving neurosurgical intervention",
    y = NULL, caption = "80% and 95% credible intervals shown in black"
  ) +
  theme_clean()

```{r canonical}
tar_load(neurosurgery_evac_can)

predictions(neurosurgery_evac_can, by = "ich_laterality")

plot_predictions(neurosurgery_evac_can, condition = "ich_laterality") +
  labs(x = "ICH Laterality", y = "Probability of Neurosurgery")

# Format things as percentage points
label_pp <- label_number(
  accuracy = 1, scale = 100,
  suffix = " pp.", style_negative = "minus"
)

label_pp_tiny <- label_number(
  accuracy = 0.01, scale = 100,
  suffix = " pp.", style_negative = "minus"
)

theme_clean <- function() {
  theme_minimal(base_family = "Barlow Semi Condensed") +
    theme(
      panel.grid.minor = element_blank(),
      plot.title = element_text(family = "BarlowSemiCondensed-Bold"),
      axis.title = element_text(family = "BarlowSemiCondensed-Medium"),
      strip.text = element_text(
        family = "BarlowSemiCondensed-Bold",
        size = rel(1), hjust = 0
      ),
      strip.background = element_rect(fill = "grey80", color = NA)
    )
}

avg_comparisons(neurosurgery_evac_can, variables = "ich_laterality") |>
  posterior_draws() |>
  ggplot(aes(x = draw)) +
  stat_halfeye(
    .width = c(0.8, 0.95), point_interval = "median_hdi",
    fill = "#bc3032"
  ) +
  scale_x_continuous(labels = label_pp) +
  labs(
    x = "Effect of hemispheric laterality\n on the probability of receiving neurosurgical intervention",
    y = NULL, caption = "80% and 95% credible intervals shown in black"
  ) +
  theme_clean()

### 2024-02-14 reports/outcomes.qmd
neurosurgery models done

# load all targets objects
tar_load_everything()

@@

outcomes_dag |>
  tidy_dagitty() |>
  node_status() |>
  ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(aes(color = status)) +
  geom_dag_edges() +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 51,
    color = "white", fontface = "bold", size = 4.5
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20")

>>>>

# load all targets objects
# tar_load_everything()
tar_load(table_1_all)
tar_load(outcomes_dag)
tar_load(ich)

@@

outcomes_dag |>
  tidy_dagitty() |>
  node_status() |>
  ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(aes(color = status)) +
  geom_dag_edges_diagonal() +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 51,
    color = "white", fontface = "bold", size = 4.5
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20")
